Honor Among Thieves^[I thank Vlad Tarko and Elana Safner for helpful comments. All remaining errors are my own.]

### 2021-08-11 ALER_cover.Rmd
ALER, and add "commons" to keywords

opening: Dear Dr. Prat,
closing: Sincerely,
address:
- Dr. Andrea Prat
- Editor-in-Chief
- Journal of Law, Economics, & Organization

@@

I am writing to submit my manuscript, "Honor Among Thieves: How 19^th^ Century American Pirate Publishers Simulated Copyright Protection." This paper shows a case study of how firms used a gap in copyright law to create their own voluntary institutions to manage a common resource — uncopyrighted foreign works in the 19th century United States.

>>>>

opening: Dear Dr. Crocco,
closing: Sincerely,
address:
- Dr. Karen Crocco
- Managing Editor
- American Law and Economics Review

@@

I am writing to submit my manuscript, "Honor Among Thieves: How 19^th^ Century American Pirate Publishers Simulated Copyright Protection" to your journal. This paper shows a case study of how firms used a gap in copyright law to create their own voluntary institutions to manage a common resource — uncopyrighted foreign works in the 19th century United States.
